S. Bikulcius Thesis: Analysis

### 2024-03-18 S. Bikulcius Thesis/analysis_report.Rmd
added standardized models

---
title: 'S. Bikulcius Thesis: Analysis'
author: "Micah E. Hirsch"
date: "2024-03-14"
output: 
  html_document:
    toc: true
    toc_float: true
    code_folding: hide

@@

@@

@@

rm(m0, m1, m2, m2b, m3, m3b, m4, m5, m6, m7, m8, m9, m10, pupil_des)

@@

>>>>

---
title: 'S. Bikulcius Thesis: Analysis'
author: "Micah E. Hirsch"
date: "2024-03-18"
output: 
  html_document:
    toc: true
    toc_float: true
    code_folding: hide

@@

##### Unstandaridized Model

@@

##### Standaridized Model

m7_standardized <- glmmTMB(scale(peak_pupil) ~ scale(trial_c) + speaker + scale(list_sort_c)*speaker + (1|subject), data = accurate_df)
sjPlot::tab_model(m7_standardized, pred.labels = c("Intercept", "Trial Order", "Speaker [ALS]", "Working Memory", 
                                      "Working Memory * Speaker [ALS]"),
                  dv.labels = "Peak Pupil Dilation",
                  file = "Tables/Peak_pupil_dilation_standardized_model.html")

@@

rm(m0, m1, m2, m2b, m3, m3b, m4, m5, m6, m7, m7_standardized, m8, m9, m10, pupil_des)

@@

##### Standaridized Model

m10_standardized <- glmmTMB(scale(effort_rating) ~ scale(trial_c) + speaker + scale(list_sort_c)*speaker + 
                scale(card_sort_c)*speaker + (trial_c|subject) + (trial_c|code), data = accurate_df)
sjPlot::tab_model(m10_standardized, pred.labels = c("Intercept", "Trial Order", "Speaker [ALS]", 
                                      "Working Memory", "Cognitive Flexibility", "Working Memory * Speaker [ALS]",
                                      "Cognitive Flexibility * Speaker [ALS]"), 
                  dv.labels = "Perceived Listening Effort",
                  file = "Tables/perceived_effort_model_standardized.html")
